Carrier phase and amplitude estimation for phase shift keying using pilots and data

### 2012-10-10 paper.tex
fixed appendix text size
fixed appendix size
fixed build script
added a bit to appendix

\appendix

@@

\begin{IEEEproof}
BLERG
\end{IEEEproof}

@@

\begin{IEEEproof}
BLERG
\end{IEEEproof}

>>>>

\normalsize
\appendix

@@

\begin{lemma}
Let $W$ be a circularly symmetric random variable with constant magnitude $Z = \abs{W} = c > 0$ and phase uniformly distributed on $[-\pi,pi)$.  Let $R \geq 0$ and $\Phi \in $ be real random variables such that $Re^{-j2\pi \Phi} = 1 + W$.  Then the pdf of $\Phi$ is
\begin{equation} \label{eq:fphicleq1}
f_{\Phi}(\phi) = \begin{cases} 
\frac{\cos(\Phi)}{\pi c} &  [-\tfrac{\pi}{2}, \tfrac{\pi}{2}] \\
0 & \text{otherwise}
\end{cases}
\end{equation}
when $0 < c \leq 1$ and
\begin{equation} \label{eq:fphicg1}
f_{\Phi}(\phi) = 
\end{equation}
when $c > 1$.
\end{lemma}
\begin{IEEEproof}
We make use of delta `function' notation and write the `pdf' of $Z$ as $\delta(z - c)$.  The pdf of $\Phi$ is then
\[
f_{\Phi}(\phi) = \int_{0}^{\infty} r \frac{\delta(z - c)}{ 2\pi z} dr = \sum_{r} \frac{r}{2\pi c}
\]
where $z^2 = r^2 - 2r\cos(\phi) + 1$ and the sum is over the positive real solutions of $c^2 = r^2 - 2r\cos(\phi) + 1$.  If $0 < c \leq 1$ and $phi \in [-\tfrac{\pi}{2}, \tfrac{\pi}{2}]$ there are two positive real solutions, these being
\[
r = \cos(\phi) \pm \sqrt{c^2 - 1 + \cos^2(\phi)},
\]
whilst if $\phi \notin [-\tfrac{\pi}{2}, \tfrac{\pi}{2}]$ there are no real solutions.  Thus~\eqref{eq:fphicleq1} holds.
\end{IEEEproof}

@@
